---
title: "ESM244 Lab 3"
author: "Anna Abelman"
date: "1/23/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)

library(tidyverse)
library(janitor)
library(here)
library(sf)
library(tmap)

```

#### Binary logistic regression

Read in data:
```{r}
gentoo <- read_csv("gentoo_lter.csv")
chinstrap <- read_csv("chinstrap_lter.csv")

penguins <- full_join(chinstrap, gentoo) %>% 
  clean_names() %>% 
  mutate(sex = str_to_lower(sex)) %>% 
  filter(sex %in% c("male", "female"))
  
```

Now let's graph this:

```{r}
ggplot(data = penguins, aes(x = sex, y = body_mass_g))+
  geom_jitter(size = 1,
              alpha = 0.5,
              aes(color = sex,
                  pch = sex))+
  facet_wrap(~species)+
  scale_color_manual(values = c("blue", "orange"))
```

Code chinstrap pengiuns as (1) and gentoo pengiuns as (0):

```{r}
penguin_bin <- penguins %>% 
  mutate(
    sp_binary = case_when(
      species == "Chinstrap penguin (Pygoscelis antarctica)" ~ 1,
      species == "Gentoo penguin (Pygoscelis papua)" ~ 0, # T ~ 3 if want to add anything else 
    )
  )
```

Now let's un out binary logistic regression:
```{r}
penguin_blr <- glm(sp_binary ~ sex +body_mass_g,
                   family = binomial,
                   data = penguin_bin)
summary(penguin_blr)
```

Let's make some predictions for penguins (classification kinda):

1. What is the probability that a penguin is a Chinstrap penguin, if it weighs 4500 grams and is male?
```{r}
df_m4500 <- data.frame(sex = "male", body_mass_g = 4500)

#find log odds of this penguin being chinstrap
m4500_logodds <- predict(penguin_blr, newdata = df_m4500, type = "link")
m4500_logodds

m4500_prob <- predict(penguin_blr, newdata = df_m4500, type = "response")
m4500_prob
#based on this data, there is a 98.28% chance that this penguin is a male chinstrap 
```

2. What is the probability that a penguin is a Chinstrap, if it is recorded as female of 4000g?

```{r}
df_f4000 <- data.frame(sex = "female", body_mass_g = 4000)
f4000_logodds <- predict(penguin_blr, newdata = df_f4000, type = "link")
f4000_logodds

f4000_prob <- predict(penguin_blr, newdata = df_f4000, type = "response")
f4000_prob
```

Now let's make an entire data frame and use it to make then visualize logistic regression outcomes:
```{r}
penguins_mock <- data.frame(
  body_mass_g = rep(seq(3000, 6000, length = 200), 2),
  sex = c(rep("male", 200), rep("female", 200))
)
```

Now let's use those to make predictions for all of them:
```{r}
full_predict <- predict(penguin_blr, newdata = penguins_mock, type = "response", se.fit = TRUE)

#get those into a data frame, along with the mock data used to create them:
final_df <- data.frame(
  penguins_mock,
  full_predict$fit,
  full_predict$se.fit
)

colnames(final_df) <- c("penguin_mass", "sex", "probability", "se")
```

Now let's graph:
```{r}
ggplot(data = final_df, aes(x = penguin_mass, y = probability))+
  geom_line(aes(color = sex))+
  geom_ribbon(aes(ymin = probability - se, 
                  ymax = probability +se,
                  fill = sex),
              alpha = 0.3)
```

#### Now some spatial data with sf

Read in the spatial data using read_sf():
```{r}
cougars <- read_sf(dsn = here("cougar_connections"), layer = "ds1014") %>%
  clean_names()
```

```{r}
large_corridors <- cougars %>% 
  filter(area_ac > 20000) %>% 
  select(area_ac)

plot(large_corridors)
```

```{r}
cougar_sub <- cougars %>% 
  select(elev_mean)
```

In ggplot:
```{r}
ggplot(data = cougar_sub)+
  geom_sf(aes(fill = elev_mean),
          color = NA)
```

```{r}
tmap_mode("view")

tm_shape(cougar_sub)+
  tm_fill("elev_mean")

```

















